This question should be answered using the `Carseats` data set 

```{r}
library(ISLR)
summary(Carseats)
```

* This is a dataset of car store locations and car prices. 

## a.b. Fit the multiple regression model to predict `Sales` using `Price`, `Urban` and `US`

```{r}
lm.ols <- lm(Sales~Price+Urban+US, data=Carseats)
summary(lm.ols)
```
* Price and US are significant. 
* There is a unit increase in sales for every -.054 units drop in price. 
* If the store is in the US there is a net increase in sales by 1.2, i.e stores in the US sell better on average than other stores by this amount. 

## c.d. Write out the model in equation form, being careful to handle the qualitative variables properly 

```
Sales = 13.04 - 0.054 * Price + -0.021 I(UrbanYes) + 1.200 * I(USYes)
```

* We can only reject the null hypothesis for values with a significantly small p value, i.e Price and USYet. We must accept it for UrbanYES (the null says there is no relationship between the predictor and the response) 

## e.f Fit a smaller model that only uses the predictors for which there is evidence of association with the outcome 

```{r}
lm.ols_sig <- lm(Sales~Price+US, data=Carseats)
summary(lm.ols_sig)
```
* Comparing this to the summary of the previous ols we see that the fit is only slightly better without the unrelated variable (based on the F statistic). 

## g. Obtain the 95% confidence intervals for the coefficients 

```{r}
confint(lm.ols_sig)
```

## h. Evidence of outliers or high leverage observations?

* outliers (don't follow trendline). Studentized residuals are all between -3 and 3 so no outliers. 
```{r}
plot(predict(lm.ols_sig), rstudent(lm.ols_sig))
```

* leverage (extreme points)
```{r}
cooksd <- cooks.distance(lm.ols_sig)
plot(cooksd, pch="*")
abline(h=4*mean(cooksd), col="red")
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T), names(cooksd), ""), col="red")
```