This problem involves simple linear regression without an intercept. 

## a. Under what circumstance is the coefficient estimate for the regression of X onto Y the same as the coefficient estimate for the regression of Y onto X? 

One clear case is when `B` = 1 
But more generally, since `B = sum[(x_i-x_bar)(y_i-y_bar)] / sum[(x_i-x_bar)^2]` for the regression of X on Y, they will be equal when `sum[(x_i-x_bar)^2] = sum[(y_i-y_bar)^2]`, i.e when the estimate of each `y` is as far from the mean of `y` as the estimate of each `x` is from the mean of `x`. 

## Geneerate an example where the coefficient for X on Y is different from Y on x_bar

```{r}
set.seed(1)
x = rnorm(100)
y = 2*x + rnorm(100)
summary(lm(y~x+0))
summary(lm(x~y+0))
```

## Generate an example in which the coefficient estimate for the regression of X onto Y is the same as the coefficient of Y onto X 

```{r}
x = rnorm(100, mean=1000, sd=0.1)
y = rnorm(100, mean=1000, sd=0.1)
summary(lm(y~x+0))
summary(lm(x~y+0))
```

The coeffients will be sufficiently close if the mean and sd of the distributions are of x and y are similar enough. 