```{r}
Auto <- read.csv("/home/beeps/rtmp/external/eco/noce/islr/labs/3/8/data/auto.csv", header=T, na.strings="?")
Auto <- na.omit(Auto)
lm.ols <- lm(mpg ~ horsepower, data=Auto)
summary(lm.ols)
confint(lm.ols)
par(mfrow=c(2,2))
plot(lm.ols)
```

## Is there a relationship between the predictor and the re-sponse?

Yes, based on the F value and its associated P value.

## How strong is the relationship between the predictor andthe response?

R^2 is 0.6, which means about 60% variance of mpg is explained by horsepower.
Another way to figure out the accuracy is to compute the RSE as a % of the mean of the mpg.
```{r}
100*4.906/mean(Auto$mpg)
```

## Is the relationship between the predictor and the response positive or negative?

Negative, see graph between `lm.ols` and `horsepower`

## What is the predicted mpg associated with a horsepower of 98? What are the associated 95 % confidence and prediction intervals?

```{r}
predict(lm.ols, data.frame(horsepower=c(98)), interval="confidence")
predict(lm.ols, data.frame(horsepower=c(98)), interval="prediction")
```

## Plot the response and the predictor. Use theabline() function to display the least squares regression line.

```{r}
plot(Auto$horsepower, Auto$mpg)
abline(lm.ols)
```
NB: abline plots (intercept, slope), which in this single variable regression is the first two coefficients. Therefore we plot horsepower on the x axis. Since its coefficient is negative, and the intercept is positive, we get a -ve trend line.
